### 2017-07-28 Paper01_EnthalpyAndCrystallization.tex
Results - Added basic deposition results

During the 35 minute depositions an average temperature rise of $3 - 4$ \degree C was observed. Nominal film thickness was about $2.5 \mu m$ giving a deposition rate of $1.2 nm/s$.

>>>>

From the 35 minute depositions a nominal film thickness of $2.5 \mu m$ was obtained, giving a deposition rate of approximately $1.2 nm/s$. The temperature within the chamber was found to rise of $3 - 4$ \degree C, significantly less than the expected $20K$ suggested by similar set ups \cite{Wang2014}.

\acrshort{eds} anaylsis showed the composition of bulk and film \MgZnCa~ was approximately the same.
